---
title: "Main Document"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(blastula)
library(stringr)
library(openfda)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gt)
library(readr)
```

# An R Markdown Document (Main Report)

This is an **R Markdown** document. *Markdown* is a simple formatting syntax for writing on the web. **R Markdown** takes this a step further by combining *Markdown* prose and **R** code into reproducible documents that can be output as HTML, PDF, Word, and many more output formats. For more details on using **R Markdown**, have a look through [its documentation site](https://rmarkdown.rstudio.com/docs/).

Let's get our data. You can also use this data in RStudio with this code:


```{r}
#this to be replaced by pins pull!

drug <- "All_Drugs"

# age <- create_age(20,65)

# jnk <- capture.output(male <- get_adverse("1", params$drug, age))
# if (!is.null(male)) {
#  male$gender <- 'male'
# }

# jnk <- capture.output(female <- get_adverse("2", params$drug, age))
# if (!is.null(female)) {
#  female$gender <- 'female'
# }

# adverse <- rbind(male, female)

# adverse <- pin_get("Adverse", board = "rsconnect") %>% group_by(term) %>% summarise(count = sum(count))

library(pins)
board <- board_register_rsconnect()
adverse <-pin_read(board, "phil-test/adverse")

```

Here is some **R** code, which is contained within a code chunk:

```{r ae_plot}

adverse %>%
  group_by(drug, term) %>% 
  summarise(count = sum(count)) %>% 
  ggplot() +
  facet_wrap(~drug) +
  geom_bar(aes(reorder(term,count), count), stat = 'identity') +
  coord_flip() +
  labs(
    x = NULL,
    y = NULL
  ) +
  theme_minimal()

```

```{r ae_table}
adverse %>%  
  mutate(term=str_to_title(term)) %>% 
  pivot_wider(names_from=gender, values_from=count) %>% 
  mutate(Total=female+male) %>% 
  top_n(10, Total) %>% 
  gt(rowname_col="term") %>% tab_header(
    title = md("Adverse Events"),
    subtitle = "The top ten most reported events"
) %>% tab_source_note("All data queried from openFDA") %>% 
  tab_stubhead(label= 'Patient Reaction') %>% 
  tab_spanner(label = "By sex",
              columns = c(female, male)) %>% 
  tab_spanner(label= 'Total Cases',
              columns = Total) %>% 
    fmt_number(columns = c(female, male, Total), sep_mark = ',', decimals=0) %>% 
  cols_label(Total = '',
             female = 'Female',
             male= 'Male')

```


It looks like the top number of adverse events for our study XYZ is: `r adverse %>% filter(count == max(count))`. Let's create a CSV for distribution (this code chunk that generates the CSV is ultimately not shown because we used `echo=FALSE` as a chunk option).

```{r write_csv, echo=FALSE}
adverse %>% write_csv("adverse.csv")
```

We can create an email on **RStudio Connect** that aligns with the content from this report. We do this with the `render_connect_email()` and `attach_connect_email()` functions from the **blastula** package. The email subdocument (`"connect-example-email.Rmd"`) is used to craft the contents of the email, drawing upon results available in this document. Attachments for the email can added by using the arguments:

- `attachments` (for any output files or included files)
- `attach_output` (which attaches the rendered report)

```{r connect_email_setup, echo=FALSE}
render_connect_email(input = "connect-example-email.Rmd") %>%
  attach_connect_email(
    subject = "RStudio Connect HTML Email",
    attach_output = TRUE,
    attachments = c("adverse.csv", "powerpoint.pptx")
  )
```

