---
title: "Adverse Events Report"
output: powerpoint_presentation
date: "`r Sys.Date()`"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library(blastula)
library(stringr)
library(openfda)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(gt)
library(readr)
```

## An R Markdown Document (Main Report)

This is an **R Markdown** document. *Markdown* is a simple formatting syntax for writing on the web. **R Markdown** takes this a step further by combining *Markdown* prose and **R** code into reproducible documents that can be output as HTML, PDF, Word, and many more output formats. For more details on using **R Markdown**, have a look through [its documentation site](https://rmarkdown.rstudio.com/docs/).

Let's get our data

```{r, include=FALSE}
#this to be replaced by pins pull!

drug <- "All_Drugs"

# age <- create_age(20,65)

# jnk <- capture.output(male <- get_adverse("1", params$drug, age))
# if (!is.null(male)) {
#  male$gender <- 'male'
# }

# jnk <- capture.output(female <- get_adverse("2", params$drug, age))
# if (!is.null(female)) {
#  female$gender <- 'female'
# }

# adverse <- rbind(male, female)

# adverse <- pin_get("Adverse", board = "rsconnect") %>% group_by(term) %>% summarise(count = sum(count))

library(pins)
board <- board_register_rsconnect()
adverse <-pin_read(board, "phil-test/adverse")

```

## plot

```{r ae_plot, echo=FALSE, message = FALSE}

adverse %>%
  group_by(drug, term) %>% 
  summarise(count = sum(count)) %>% 
  ggplot() +
  facet_wrap(~drug) +
  geom_bar(aes(reorder(term,count), count), stat = 'identity') +
  coord_flip() +
  labs(
    x = NULL,
    y = NULL
  ) +
  theme_minimal()



```

## data

```{r greater_30000_ae, echo=FALSE, message = FALSE}
adverse %>% filter(count > 30000)
```


