---
title: 'Getting Started'
output: html_notebook
---

# Adverse Events

## Accessing Data

```{r setup}
library(flexdashboard)
library(openfda)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(purrr)
```

Next, we'll write some helper functions to use the openFDA API and package to query adverse events data.
```{r}
get_adverse <- function(gender, brand_name, age) {
  my_query <- fda_query("/drug/event.json")

  map_df(c("Aspirin", "Fexofenadine", "Etanercept"), function(drug) {
    df = my_query %>%
    fda_filter("patient.patientsex", gender) %>% 
    fda_filter("patient.drug.openfda.generic_name", drug) %>% 
    fda_count("patient.reaction.reactionmeddrapt.exact") %>% 
    fda_limit(10) %>% 
    fda_exec()
    df$drug = drug
    df
  })
}

create_age <- function(min, max){#
  sprintf('[%d+TO+%d]', min, max)
}
```



Using our openFDA helper functions, we can pull adverse event data by gender for a specific drug and age range. We can also lookup the drug's active ingredients.

```{r pull-data}
# specify drug
# c("Aspirin", "Fexofenadine", "Clonazepam")
drug <- "Aspirin"

# specify age range
age <- create_age(20,65)

# get adverse event data from the openfda API
jnk <- capture.output(male <- get_adverse("1", drug, age))
if (!is.null(male)) {
  male$gender <- 'male'
}
jnk <- capture.output(female <- get_adverse("2", drug, age))
if (!is.null(female)) {
  female$gender <- 'female'
}

# comnbine male and female event data
adverse <- rbind(male, female)

adverse
```


## Publish Pin
```{r}
# remotes::install_github("rstudio/pins")
library(pins)

# depends on CONNECT_SERVER and CONNECT_API_KEY variable
board <- board_register_rsconnect()

board %>% pin_write(adverse, "adverse", type = "csv")
```


## Plotting

Now we're ready to start investigating the data and showing off the resulting graphics. We'll create plots and then a static dashboard.

```{r plots}
# plot all events  
adverse %>%
  group_by(drug, term) %>% 
  summarise(count = sum(count)) %>% 
  ggplot() +
  facet_wrap(~drug) +
  geom_bar(aes(reorder(term,count), count), stat = 'identity') +
  coord_flip() +
  labs(
    x = NULL,
    y = NULL
  ) +
  theme_minimal()
  
```

```{r gender}
  # plot by gender for one drug
adverse %>%
  filter(drug == drug) %>%
ggplot() +
  geom_bar(aes(reorder(term,count), count, fill = gender), stat = 'identity') +
  facet_wrap(~gender)+
  coord_flip() +
  labs(
    title = drug,
    x = NULL,
    y = NULL
  ) +
  theme_minimal() + 
  guides(fill = FALSE) + 
  scale_fill_manual(values = c("#d54a30","#4c83b6"))
  
```
