---
title: 'Getting Started'
output: html_notebook
---

# Adverse Events

## Accessing Data

```{r setup}
library(flexdashboard)
library(openfda)
library(dplyr)
library(ggplot2)
library(ggthemes)
library(purrr)
```

Next, we'll write some helper functions to use the openFDA API and package to query adverse events data.
```{r}
get_adverse <- function(gender, brand_name, age) {
  my_query <- fda_query("/drug/event.json")

  map_df(c("Aspirin", "Fexofenadine", "Clonazepam"), function(drug) {
    df = my_query %>%
    fda_filter("patient.drug.openfda.generic_name", drug) %>% 
    fda_filter("patient.patientonsetageunit", "801") %>% 
    fda_count("patient.patientonsetage") %>% 
    fda_count("patient.reaction.reactionmeddrapt.exact") %>% 
    fda_limit(10) %>% 
    fda_exec()
    df$drug = drug
    df
  })
}

create_age <- function(min, max){#
  sprintf('[%d+TO+%d]', min, max)
}
```




```{r openfda}
# Helper Functions
# get_adverse <- function(gender, brand_name, age) {
#  fda_query("/drug/event.json") %>%
#    fda_filter("patient.drug.openfda.brand_name", brand_name) %>% 
#    fda_filter("patient.patientsex", gender) %>% 
#    fda_filter("patient.patientonsetage", age) %>% 
#    fda_count("patient.reaction.reactionmeddrapt.exact") %>% 
#    fda_limit(10) %>% 
#    fda_exec()
#}


#create_age <- function(min, max){#
#  sprintf('[%d+TO+%d]', min, max)
#}

```

Using our openFDA helper functions, we can pull adverse event data by gender for a specific drug and age range. We can also lookup the drug's active ingredients.

```{r pull-data}
# specify drug
# c("Aspirin", "Fexofenadine", "Clonazepam")
drug <- "Aspirin"

# specify age range
age <- create_age(20,65)

# get adverse event data from the openfda API
jnk <- capture.output(male <- get_adverse("1", drug, age))
if (!is.null(male)) {
  male$gender <- 'male'
}
jnk <- capture.output(female <- get_adverse("2", drug, age))
if (!is.null(female)) {
  female$gender <- 'female'
}

# comnbine male and female event data
adverse <- rbind(male, female)

adverse
```

## Publish Pin
```{r}
library(pins)

# pins::board_register_rsconnect()

board <- board_rsconnect(auth = "envvar", account = "gt", server = "http://ec2-18-216-69-78.us-east-2.compute.amazonaws.com/rsconnect/",
               key = "CkOOl2oN1nNpifYPqowht7QMuTIWeKLc")

board %>% pin_write(adverse, "adverse", type = "csv")
```


## Publish Pin Securly
```{r}
# library(pins)

# pins::board_register_rsconnect()


# board <- board_rsconnect(
#    auth = "envvar",
#    server = Sys.getenv("CONNECT_SERVER"), # Sys.getenv("CONNECT_SERVER")
#    account = "gt",
#    key = Sys.getenv("VETIVER_API"))

# board %>% pin_write(adverse, "adverse", type = "csv")

```

## Plotting

Now we're ready to start investigating the data and showing off the resulting graphics. We'll create plots and then a static dashboard.

```{r plots}
# plot all events  
adverse %>% filter(drug == drug) %>%
  group_by(term) %>% 
  summarise(count = sum(count)) %>% 
  ggplot() +
  geom_bar(aes(reorder(term,count), count), stat = 'identity') +
  coord_flip() +
  labs(
    title = drug,
    x = NULL,
    y = NULL
  ) +
  theme_minimal()
  
```

```{r gender}
  # plot by gender
ggplot(adverse) +
  geom_bar(aes(reorder(term,count), count, fill = gender), stat = 'identity') +
  facet_wrap(~gender)+
  coord_flip() +
  labs(
    title = drug,
    x = NULL,
    y = NULL
  ) +
  theme_minimal() + 
  guides(fill = FALSE) + 
  scale_fill_manual(values = c("#d54a30","#4c83b6"))
  
```
