---
title: "Immunogenicity - Reporting Positive Samples"
output: html_document
params:
  screening_cut_point: 200
  confirmatory_cut_point: 20
---

ADA _three‐tiered_ testing strategy is deployed here to assess ADA. Set screening and confirmatory cut-points in the rmd file at top.

### ADA Three‐tiered Testing Method

## Example one

The Screening cut-point is: `r params$screening_cut_point`

The Confirmatory cut-point is: `r params$confirmatory_cut_point`

```{r, echo=FALSE, include=FALSE, message=FALSE, warning=FALSE}
#packages
library(tidyverse)
library(magrittr)
library(stringr)
library(plotly)
library(crosstalk)
library(DT)
```

# Screening Data
```{r, message=FALSE, warning=FALSE, include=FALSE,}

# readr
Screening <- read_csv("Sample_ADA_Data_05062017_Screening.csv") %>% mutate(Screening_Cutpoint = params$screening_cut_point) %>%
  mutate(Screening_Result_Drug = ifelse(Signal_Response_No_Drug > Screening_Cutpoint, "Positive", "Negative")) %>% mutate(Signal_Response_No_Drug_log10 = log10(Signal_Response_No_Drug)) %>% filter(Screening_Result_Drug=="Positive")

datatable(Screening, options = list(pageLength = 10))
```

# Confirmatory Data
```{r, message=FALSE, warning=FALSE, include=FALSE,}

# readr
Confirmatory <- read_csv("Sample_ADA_Data_05062017_Confirmatory.csv")

Screening_Confirmatory <- Screening %>%
  left_join(Confirmatory, by = 'Sample_Number') %>%
mutate(Signal_Response_Difference = Signal_Response_No_Drug - Signal_Response_Drug)  %>% mutate(Signal_Response_Divide = Signal_Response_Difference / Signal_Response_No_Drug)  %>%
  mutate(Percent_Signal_Inhibition_Drug = Signal_Response_Divide * 100) %>% mutate(Confirmatory_Cutpoint = params$confirmatory_cut_point) %>%
  mutate(Confirmatory_Result_Drug = ifelse(Percent_Signal_Inhibition_Drug > Confirmatory_Cutpoint, "Positive", "Negative")) %>% select(-Signal_Response_Difference, -Signal_Response_Divide)%>% filter(Confirmatory_Result_Drug=="Positive")

datatable(Screening_Confirmatory, options = list(pageLength = 10))

```

# Add Titer to Confirmatory Data
```{r, message=FALSE, warning=FALSE, include=FALSE,}

Titer <- read_csv("Sample_ADA_Data_05062017_Titer.csv")

Screening_Confirmatory_Titer <- Screening_Confirmatory %>%
  left_join(Titer, by = 'Sample_Number') 

# %>% filter(Screening_Result_Drug=="Positive" & Confirmatory_Result_Drug=="Positive")

datatable(Screening_Confirmatory_Titer, options = list(pageLength = 10))

```

Plots of positive screening signal response and percent signal inhibition & screening signal response and titer

```{r, echo=FALSE, message=FALSE, warning=FALSE}
d <- SharedData$new(Screening_Confirmatory_Titer)
s <- subplot(
  qplot(data = d, x = Signal_Response_No_Drug, y = Percent_Signal_Inhibition_Drug),
  qplot(data = d, x = Signal_Response_No_Drug, y = Reported_Titer)
)

highlight(s, "plotly_selected")
```

Plot of Postive Signal_Response_No_Drug and Percent_Signal_Inhibition_Drug
```{r, echo=FALSE, message=FALSE, warning=FALSE}
p <- qplot(Signal_Response_No_Drug, Percent_Signal_Inhibition_Drug, data=Screening_Confirmatory_Titer, colour=Screening_Result_Drug)

p <- ggplotly(p)

p
```

Distribution of Signal_Response_No_Drug for true positives
```{r, echo=FALSE, message=FALSE, warning=FALSE}

p = ggplot(Screening_Confirmatory_Titer, aes(x=Signal_Response_No_Drug)) +
    geom_histogram(aes(y = ..density..), binwidth=density(Screening_Confirmatory_Titer$Signal_Response_No_Drug)$bw) +
    geom_density(fill="red", alpha = 0.2)

p = ggplotly(p)

p

```

Distribution of Signal_Response_No_Drug Log 10 transformed for true positives
```{r, echo=FALSE, message=FALSE, warning=FALSE}

p = ggplot(Screening_Confirmatory_Titer, aes(x=Signal_Response_No_Drug_log10)) +
    geom_histogram(aes(y = ..density..), binwidth=density(Screening_Confirmatory_Titer$Signal_Response_No_Drug_log10)$bw) +
    geom_density(fill="red", alpha = 0.2)

p = ggplotly(p)

p

```


