---
title: "Email Document"
output: blastula::blastula_email
---

```{r packages, include=FALSE}
library(tidyverse)
```

# An R Markdown Document (Summary Report for Email)

It looks like the top number of adverse events for our study XYZ is: `r adverse %>% filter(count == max(count))`. Let's create a CSV for distribution (this code chunk that generates the CSV is ultimately not shown because we used `echo=FALSE` as a chunk option).

We can include parts from the parent `"connect-example-main.Rmd"` document by adding an empty R Markdown code chunk with a matching name (in this case `diamonds_plot`). This is great because we can reuse parts from the parent report document.

```{r ae_plot, echo=FALSE}
```

The AE table (from the parent document's `ae_table` chunk) can be included in the same way:

```{r ae_table, echo=FALSE}
```

Note that the `echo=FALSE` parameter was added to each of the the code chunks to prevent printing of the **R** code that generated the plot (we just want the output for the email).

The `adverse` object (from the namesake **R** code chunk) is also available and can be further processed to generate different output just for the email document.

```{r greater_1000_ae, echo=FALSE}
adverse %>% filter(count > 1000)
```
